manuscript_figures

### 2024-06-17 scripts/data_cleaning.Rmd
working on filtering QUAD data

# use rbind.fill() method in R to combine data frames with different columns
QUAD_data <- rbind.fill(QUAD_long, QUAD_2018, FtWeatherill_QUAD_2017, FtWeatherill_QUAD_2016_TALBENHORIN)

@@

# use rbind.fill() method in R to combine data frames with different columns
rug_data <- rbind.fill(rugosity_2019_DEM, rugosity_2020_DEM, rugosity_2021_DEM)

#remove 22-25 columns for observers not needed information
rug_data <- rug_data[ -c(22:25) ]

# Rename Kings Beach to King's Beach
rug_data$SITE[rug_data$SITE == "Kings Beach"] <- "King's Beach"
rug_data$SITE[rug_data$SITE == "KB"] <- "King's Beach"

>>>>

)# use rbind.fill() method in R to combine data frames with different columns
QUAD_data <- rbind.fill(QUAD_long, QUAD_2018, FtWeatherill_QUAD_2017, FtWeatherill_QUAD_2016_TALBENHORIN)

@@

kelp_rug_2022 <- data.frame(YEAR = 2022, kelp_rugosity_2022)

kelp_rug_2023 <- data.frame(YEAR = 2023, kelp_rugosity_2022)

# use rbind.fill() method in R to combine data frames with different columns
rug_data <- rbind.fill(rugosity_2019_DEM, rugosity_2020_DEM, rugosity_2021_DEM, kelp_rug_2022, kelp_rug_2023)

#remove 22-25 columns for observers not needed information
rug_data <- rug_data[ -c(21:25) ]

# Rename Kings Beach to King's Beach
rug_data$SITE[rug_data$SITE == "Kings Beach"] <- "King's Beach"
rug_data$SITE[rug_data$SITE == "KB"] <- "King's Beach"
rug_data$SITE[rug_data$SITE == "Fort Weatherill"] <- "Fort Wetherill"
rug_data$SITE[rug_data$SITE == "Ft. Weatherill"] <- "Fort Wetherill"
rug_data$TRANSECT[rug_data$TRANSECT == "Control 1"] <- "1"
rug_data$TRANSECT[rug_data$TRANSECT == "Control 2"] <- "2"

### 2024-06-17 scripts/manuscript_figures.Rmd
working on filtering QUAD data

@@

@@

# Compute the correlation matrix using Spearman correlation
cormat <- round(cor(all.params.data, method = "spearman"), 4)
head(cormat)

@@

## Calculate p-values
p_values <- cor.mtest(all.params.data, method = "spearman")$p

@@

#view results of model
summary_text1 <- capture.output(summary(fit1))
writeLines(summary_text1, "output/figures/summary_original_model.txt")

# Fit a multiple regression model with site and year as interactions
fit2 <- lm(Fish_Biomass ~ Rugosity * Kelp_Biomass * Kelp_Cover * SITE * YEAR, data = all.params.data)

# Diagnostic plots for the regression model
par(mfrow=c(2,2))
plot(fit2)

#view results of model
summary_text2 <- capture.output(summary(fit2))
writeLines(summary_text2, "output/figures/summary_model_site_year_fixed.txt")

@@

# Try another type of multiple regession plot
```{r}
#fit multiple linear regression model WITH SITE AND YEAR
fit3 <- lm(Fish_Biomass ~ SITE*YEAR, data = all.params.data)

#view results of model
summary_text3 <- capture.output(summary(fit3))
writeLines(summary_text3, "output/figures/summary_model_site_year_fixed_fishbiomass.txt")

# Fit the mixed-effects model
fit4 <- lmer(log(Fish_Biomass) ~ log(Rugosity) * log(Kelp_Biomass) * log(Kelp_Cover) + 
              (1 | SITE) + (1 | YEAR), data = all.params.data)

#view results of model
summary_text4 <- capture.output(summary(fit4))
writeLines(summary_text4, "output/figures/summary_model_site_year_random.txt")

@@

# run with just site as random effect
# Fit the mixed-effects model
fit5 <- lmer(log(Fish_Biomass) ~ log(Rugosity) * log(Kelp_Biomass) * log(Kelp_Cover) + 
              (1 | SITE), data = all.params.data)

#view results of model
summary_text5 <- capture.output(summary(fit5))
writeLines(summary_text5, "output/figures/summary_model_site_random.txt")

@@

# run with just year as random effect
# Fit the mixed-effects model
fit6 <- lmer(log(Fish_Biomass) ~ log(Rugosity) * log(Kelp_Biomass) * log(Kelp_Cover) + 
              (1 | YEAR), data = all.params.data)

#view results of model
summary_text6 <- capture.output(summary(fit6))
writeLines(summary_text6, "output/figures/summary_model_year_random.txt")

>>>>

# edited control transcet name
mean_rugosity$TRANSECT[mean_rugosity$TRANSECT == "Control 2"] <- "2"

@@

# Filter quad data for all inverts and use to correlate to fish biomass
```{r}

@@

# Select the relevant columns
selected_columns <- all.params.data[, c("Fish Biomass (g/cm2)", "Kelp Biomass (g/cm2)", "Rugosity", "Kelp Cover (%)")]

# Calculate the Spearman correlation matrix
cormat <- round(cor(selected_columns, method = "spearman", use = "complete.obs"), 4)
head(cormat)

@@

## Calculate p-values
p_values <- cor.mtest(selected_columns, method = "spearman")$p

@@

#view results of model
summary_text1 <- capture.output(summary(fit1))
writeLines(summary_text1, "output/figures/summary_original.model.txt")

@@

# Try another type of multiple regession plot
```{r}
#fit multiple linear regression model WITH SITE AND YEAR
fit2 <- lm(Fish_Biomass ~ SITE*YEAR, data = all.params.data)

#view results of model
summary_text2 <- capture.output(summary(fit2))
writeLines(summary_text2, "output/figures/summary_model_site_year_fixed_fishbiomass.txt")

# Fit the mixed-effects model
fit3 <- lmer(log(Fish_Biomass) ~ log(Rugosity) * log(Kelp_Biomass) * log(Kelp_Cover) + 
              (1 | SITE) + (1 | YEAR), data = all.params.data)

#view results of model
summary_text3 <- capture.output(summary(fit3))
writeLines(summary_text3, "output/figures/summary_model_site_year_random.txt")

@@

# run with just site as random effect
# Fit the mixed-effects model
fit4 <- lmer(log(Fish_Biomass) ~ log(Rugosity) * log(Kelp_Biomass) * log(Kelp_Cover) + 
              (1 | SITE), data = all.params.data)

#view results of model
summary_text4 <- capture.output(summary(fit4))
writeLines(summary_text4, "output/figures/summary_model_site_random.txt")

@@

# run with just year as random effect
# Fit the mixed-effects model
fit5 <- lmer(log(Fish_Biomass) ~ log(Rugosity) * log(Kelp_Biomass) * log(Kelp_Cover) + 
              (1 | YEAR), data = all.params.data)

#view results of model
summary_text5 <- capture.output(summary(fit5))
writeLines(summary_text5, "output/figures/summary_model_year_random.txt")
